---
title: "A really not so simple document"
author: "Jeff Goldsmith"
date: 2026-09-17
output: html_document
---

I'm an R Markdown document! 

```{r echo = TRUE, message = FALSE}
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is where I'm going to talk about code chunks.

```{r eval = FALSE}
mean(samp)
sd(samp)
```

Let's also make a dataframe.

```{r}
example_df = 
  tibble(
    vec_numeric = 1:4,
    vec_char = c("My", "name", "is", "jeff"),
    vec_factor = factor(c("male", "male", "female", "female"))
  )
```

I'll create a new dataframe.

```{r}
new_df = 
  tibble(
    x = rnorm(100),
    y = 1 + 2 * x + rnorm(100)
  )
```

Let's make a plot and see how cool that is!

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, mean = 1, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This is a neat scatterplot!!!


What if I try to add a histogram?

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

